### 2022-06-30 letter.tex
Update content

\documentclass[11pt]{letter} % Default font size of the document, change to 10pt to fit more text
\usepackage[sfdefault]{noto}

% margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
%\date{yyyy-mm-dd}
\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right
\raggedbottom

\begin{document}

\begin{letter}{
theirname \\
theirtitle \\
theircompany \\
theirstreet1 \\
theirstreet2 \\
theircity~ theirstate~~ theirzip
}

myname \\
mytitle \\
mystreet1 \\
mystreet2 \\
mycity~ mystate~~ myzip \\
phone \\
email
% \vfill

\signature{myname}

% letter content
\opening{subject \\ \\ Dear Sir or Madam:}

@@

\closing{Regards,}

\encl{document1, document2, document3}

\end{letter}
\end{document}

>>>>

\documentclass[11pt]{letter}
\usepackage[sfdefault]{noto}
\topmargin=-1in
\textheight=10in
\oddsidemargin=-10pt
\textwidth=6.5in
\date{yyyy-mm-dd}
\let\raggedleft\raggedright
\raggedbottom
\signature{myname}

\begin{document}
\begin{letter}{
theirname \\
theirtitle \\
theircompany \\
theirstreet1 \\
theirstreet2 \\
theircity\ \ theirstate\ \ \ \ theirzip
}

myname \\
mytitle \\
mystreet1 \\
mystreet2 \\
mycity~ mystate~~ myzip \\
phone \\
email

\opening{subject \\ \\ Dear theirname:}

@@

\closing{Regards,}
\encl{document1, document2, document3}
\end{letter}
\end{document}
